% SampleProject.tex -- main LaTeX file for sample LaTeX article
%
%\documentclass[12pt]{article}
\documentclass[11pt]{SelfArxOneColBMN}
% add the pgf and tikz support.  This automatically loads
% xcolor so no need to load color
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{matrix}
\usetikzlibrary{calc}
\usepackage{xstring}
\usepackage{pbox}
\usepackage{etoolbox}
\usepackage{marginfix}
\usepackage{xparse}
\setlength{\parskip}{0pt}% fix as marginfix inserts a 1pt ghost parskip
% standard graphics support
\usepackage{graphicx,xcolor}
\usepackage{wrapfig}
%
\definecolor{color1}{RGB}{0,0,90} % Color of the article title and sections
\definecolor{color2}{RGB}{0,20,20} % Color of the boxes behind the abstract and headings
%----------------------------------------------------------------------------------------
% HYPERLINKS
%----------------------------------------------------------------------------------------
\usepackage[pdftex]{hyperref} % Required for hyperlinks
\hypersetup{hidelinks,
colorlinks,
breaklinks=true,%
urlcolor=color2,%
citecolor=color1,%
linkcolor=color1,%
bookmarksopen=false%
,pdftitle={Exam 3 Sample},%
pdfauthor={Peterson}}
%\usepackage[round,numbers]{natbib}
\usepackage[numbers]{natbib}
\usepackage{lmodern}
\usepackage{setspace}
\usepackage{xspace}
%
\usepackage{subfigure}
\newcommand{\goodgap}{
  \hspace{\subfigtopskip}
  \hspace{\subfigbottomskip}}
%
\usepackage{atbegshi}
%
\usepackage[hyper]{listings}
%
% use ams math packages
\usepackage{amsmath,amsthm,amssymb,amsfonts}
\usepackage{mathrsfs}
%
% use new improved Verbatim
\usepackage{fancyvrb}
%
\usepackage[titletoc,title]{appendix}
%
\usepackage{url}
%
% Create length for the baselineskip of text in footnotesize
\newdimen\footnotesizebaselineskip
\newcommand{\test}[1]{%
 \setbox0=\vbox{\footnotesize\strut Test \strut}
 \global\footnotesizebaselineskip=\ht0 \global\advance\footnotesizebaselineskip by \dp0
}
%
\usepackage{listings}

\DeclareGraphicsExtensions{.pdf, .jpg, .tif,.png}

% make sure we don't get orphaned words if at top of page
% or orphans if at bottom of page
\clubpenalty=9999
\widowpenalty=9999
\renewcommand{\textfraction}{0.15}
\renewcommand{\topfraction}{0.85}
\renewcommand{\bottomfraction}{0.85}
\renewcommand{\floatpagefraction}{0.66}
%
\DeclareMathOperator{\sech}{sech}

\input{setupsample}

\JournalInfo{MATH 8210:  Exam 3 Sample, 1-\pageref{LastPage}, 2020} % Journal information
\Archive{Draft Version \today} % Additional notes (e.g. copyright, DOI, review/research article)

\PaperTitle{MATH 8210 Exam 3 Sample}
\Authors{Ian Davis\textsuperscript{1}}
\affiliation{\textsuperscript{1}\textit{John E. Walker Department of Economics,
Clemson University,Clemson, SC: email ijdavis@g.clemson.edu}}

\date{\small{Version ~\today}}
\Abstract{Exam 3 Sample}
\Keywords{}
\newcommand{\keywordname}{Keywords}
%
\onehalfspacing
\begin{document}

\flushbottom

\addcontentsline{toc}{section}{Title}
\maketitle

\renewcommand{\theexercise}{\arabic{exercise}}%

\textbf{Part One: Definitions}
\begin{enumerate}
  \item Define what an inner product on the set X is carefully. Do this for both the real and complex field.
  \begin{solution}
    \begin{itemize}
      \item Real Inner Product\\
      Let V be a vector space with the reals as the scalar field. Then a mapping $\omega$ which assigns a pair of objects to a real number is called an inner product on V if
      \begin{enumerate}
        \item $\omega(\mathbf{u,v}) = \omega(\mathbf{u,v})$; that is, the order is not important for any two objects.
        \item $\omega(c\odot\mathbf{u,v}) = c\omega(\mathbf{u,v}$); that is, scalars in the first slot can be pulled out.
        \item $\omega(\mathbf{u} \oplus \mathbf{w,v}) = \omega(\mathbf{u,v}) + \omega(\mathbf{w,v})$; for any three objects
        \item $\omega(\mathbf{u,u}) \geq 0$ and $\omega(\mathbf{u,u}) = 0 \iff u = 0$
      \end{enumerate}
      These properties imply that $\omega(\mathbf{u},c\odot\mathbf{v} = c\omega(\mathbf{u,v})$ as well. A vector space V with an inner product is called a real inner product space.
      \item Complex Inner Product space\\
      Let V be a vector space with the complex numbers as the scalar field. Then a mapping $\omega$ which assigns a pair of objects to a complex number is called and inner product on V if
      \begin{enumerate}
        \item $\omega(\mathbf{u,v}) = \overline{\omega(\mathbf{u,v})}$; that is, the order is important. Switching the order conjugates the result.
        \item $\omega(c\odot\mathbf{u,v}) = c\omega(\mathbf{u,v}$); that is, scalars in the first slot can be pulled out. Using IPC1, this implies
        \begin{eqnarray*}
          \omega(\mathbf{u},c\odot\mathbf{v}) = \overline{\omega(c\odot\mathbf{v},\mathbf{u})} = \overline{c\omega(\mathbf{u,v})} = \overline{c}\omega(\mathbf{u,v})
        \end{eqnarray*}
        \item $\omega(\mathbf{u} \oplus \mathbf{w,v}) = \omega(\mathbf{u,v}) + \omega(\mathbf{w,v})$; for any three objects
        \item $\omega(\mathbf{u,u}) \geq 0$ and $\omega(\mathbf{u,u}) = 0 \iff u = 0$
      \end{enumerate}
      A vector space V with a complex inner product is  called a \textbf{Complex Inner Product Space}.
    \end{itemize}
  \end{solution}
  \item Describe how to complete $(C([a,b]),d_2)$ in reasonable detail.
  \begin{solution}
    1. Define
    \begin{eqnarray*}
      S = \{(x_n)\;|\;x_n \in C([a,b]),\;(x_n)\text{ is a Cauchy Sequence in }(C([a,b]),d_2)\}
    \end{eqnarray*}
    2. Define an equivalence relation on S by
    \begin{eqnarray*}
      (x_n) \sim (y_n) \iff lim_{n\rightarrow\infty}d_2(x_n,y_n) = 0
    \end{eqnarray*}
    3. Let $\widetilde{C}([a,b]) = S/\sim$, the set of all equivalence classes in S under $\sim$. Let the elements of $\widetilde{C}([a,b])$ be denoted by $[(x_n)]$.\\
    4. Extend the metric $d_2$ on X to the metric $\widetilde{d}_2$ by defining 
    \begin{eqnarray*}
      \widetilde{d}_2(\widetilde{x},\widetilde{y}) = lim_{n\rightarrow\infty}d_2(x_n,y_n)
    \end{eqnarray*}
    for any equivalence class $\widetilde{x}$ and $\widetilde{y}$ in $\widetilde{X}$ and any choice of representatives $(x_n) \in \widetilde{x}$ and $(y_n) \in \widetilde{y}$.\\
    5. Define the mapping $T: C([a,b])rightarrow \widetilde{C}([a,b])$ by $T(x) = [(\widetilde{x}])$ where $\bar{x} = (x,x,x,...)$ is the constant sequence. Note each entry $x$ is actually a continuous function on $[a,b]$. Then $T$ is $1 -1$, onto, and isometric.\\
    6. $T(C([a,b]))$ is dense in $(\widetilde{C}([a,b]),\widetilde{d}_2)$\\
    7. $(\widetilde{C}([a,b]),\widetilde{d}_2)$ is complete.
  \end{solution}
  \item Define a bounded linear operator $T$ between the normed linear spaces $(X,\|\cdot\|_X)$ and $(Y,\|\cdot\|_Y)$.
  \begin{solution}
    Let $T: dom(T) \subset (X,||\cdot||_X) \rightarrow (Y,||\cdot||_X)$ be a linear operator (i.e.) mapping on the subspace $dom(T)$. We say $T$ is a bounded linear ($T(\alpha x + \beta y) = \alpha T(X) + \beta T(y)$) operator if
    \begin{eqnarray*}
      B(T) = sup_{x\in dom(T), x\neq0} \frac{||T(x)||_Y}{||x||_X} < \infty
    \end{eqnarray*}
    Since $T$ is linear
    \begin{eqnarray*}
      \frac{||T(x)||_Y}{||x||_X} = T(\frac{x}{||x||_X})
    \end{eqnarray*}
    and so an equivalent way to define $B(T)$ is
    \begin{eqnarray*}
      B(T) = sup_{x\in dom(T),||x||_X = 1}||T(x)||_Y
    \end{eqnarray*}
  \end{solution}
  \item Define what it means for a family of functions to be equicontinuous.
  \begin{solution}
    Let $F$ be a family of functions in the space $C([a,b])$ for a finite interval $[a,b]$. The family is equicontinuous at $t_0$ in $[a,b]$ if for all $\epsilon > 0$, there is a $\delta > 0$ so that for all $f \in F$,
    \begin{eqnarray*}
      |t - t_0| < \delta \implies \\
      |f(t_0) - f(t)| < \epsilon
    \end{eqnarray*}
    The family is uniformly equicontinuous if for all $\epsilon > 0$, there is a $\delta > 0$ so that for all $f \in F$,
    \begin{eqnarray*}
      |s - t_0| < \delta \implies\\
      |f(s) - f(t)| < \epsilon
    \end{eqnarray*}
  \end{solution}
  \item Define what a Schauder Basis means for a normed linear space.
  \begin{solution}
    Let $(X,\|\cdot\|)$ be a non empty normed linear space. Let $M = (m_n)_{n=1}^\infty$ be a countable subset of X so that given $x \in X$n there is a unique sequence of scalars $(\alpha_n)_{n=1}^\infty$ so that $x = lim_{n\rightarrow\infty}\sum_{j=1}^N\:\alpha_jm_j$. This says $x = \sum_{j=1}^N\:\alpha_jm_j$ is an infinite series in $X$, whose partial sums converge in norm to $x$. This set $M$ is called a Schauder Basis for $X$. 
  \end{solution}
  \item Define what it means for a set $D$ in a metric space to be dense.
  \begin{solution}
    Let $(X,d)$ be a metric space and let $D \subset X$. We say D is dense in $X$ if for all $\varepsilon > 0$, if given $x \in X$, there is a $y \in D$ so that $d(x,y) < \varepsilon$. This implies given $x \in X$, there is a sequence $y_n$ so that $y_n \rightarrow x$ in the $d$ metric. 
  \end{solution}
  \item Define what it means for a metric space $D$ to be separable.
  \begin{solution}
    We say $D$ is a seperable subspace of the metric space (X,d) if $D$ is countable and dense in X
  \end{solution}
  \item Define the dual space of the normed linear space $(X,\|\cdot\|_X)$.
  \begin{solution}
    The  dual of the normed linear space $(X,\|\cdot\|_X)$ is $X' = B(X,F)$ where F is the underlying field and 
    \begin{eqnarray*}
      B(X,F) = \{f: X \rightarrow F\;|\;f\text{ is continuous and linear}\} = \{f: X \rightarrow F\;|\;f\text{ is bounded and linear}\} 
    \end{eqnarray*}
  \end{solution}
  \item Define the double dual space of the normed linear space $(X,\|\cdot\|_X)$.
  \begin{solution}
    The double dual of the normed linear space $(X,\|\cdot\|_X)$ is $X'' = B(B(X,F),F)$ where F is the underlying field and $B(B(X,F),F)$
    \begin{eqnarray*}
      B(B(X,F),F) = \{g: X' \rightarrow F\;|\;g\text{ is continuous and linear}\} = \{g: X' \rightarrow F\;|\;g\text{ is bounded and linear}\} 
    \end{eqnarray*}
  \end{solution}
\end{enumerate}

\textbf{Part Two: Theorems and Lemmas}
\begin{enumerate}
  \item State the Parallelogram Equality.
  \begin{solution}
    Let $(X,<\cdot,\cdot>)$ be an inner product space. Then the norm induced by the inner product satisfies the parallelogram Equality:
    \begin{eqnarray*}
      \|(\mathbf{x} + \mathbf{y})\|^2 + \|(\mathbf{x} - \mathbf{y})\|^2 = 2(\|x\|^2 + \|y\|^2)
    \end{eqnarray*}
    for all $\mathbf{x}$ and $\mathbf{y}$ in X.
  \end{solution}
  \item State the Cauchy - Schwartz Ineqaulity
  \begin{solution}
    \begin{itemize}
      \item Real Inner Product Space\\
      If V is an inner product space with real inner product $<\cdot,\cdot>$ and induced norm $\|\cdot\|$, then
      \begin{eqnarray*}
        |<\mathbf{u},\mathbf{v}> \leq \|\mathbf{u}\|\|\mathbf{v}\|
      \end{eqnarray*}
      with equality occuring if and only if $\mathbf{u}$ and $\mathbf{v}$ are linearly dependent.
      \item Complex Inner Product Space
      If V is an inner product space with complex inner product $<\cdot,\cdot>$ and induced norm $\|\cdot\|$, then
      \begin{eqnarray*}
        |<\mathbf{u},\mathbf{v}> \leq \|\mathbf{u}\|\|\mathbf{v}\|
      \end{eqnarray*}
      where $|\cdot|$ here is the complex magnitude and with equality occuring if and only if $\mathbf{u}$ and $\mathbf{v}$ are linearly dependent.
    \end{itemize}
  \end{solution}
\end{enumerate}

\textbf{Part Three: Is it Possible and Short Answer}
\begin{enumerate}
  \item Give an example of a norm that cannot be induced by an inner product.
  \item If $T$ is an operator from $dom(T) \subset (X,\|\cdot\|_X)$ into $(Y,\|\cdot\|_Y)$, not necessarily linear, is it posible for $T$ to be bounded? Give an example.
  \item Is it true the dual space of the normed linear space $(X,\|\cdot\|_X)$ must be complete?
  \item Is it true that Riemann integration on $[a,b]$ defines an element of the duel space of $(C([a,b]),\|\cdot\|)$?
  \item Is it that given $\mathbf{x} \in \mathcal{R}^n$, the function $f$ defined by $f(\mathbf{y}) = <\mathbf{x},\mathbf{y}>$ is an element of $\mathcal{R}^n$?
  \item If A is an $n \times n$ symmetric matrix, is it true that $\|A\| < \max_{\|x\| = 1}|<A(x),x)>$?
\end{enumerate}

\textbf{Part Four: Proofs}
Provide careful proofs of the following propositions.
\begin{enumerate}
  \item Let $A =
  \begin{bmatrix}
    2 & 4\\
    4 & 3\\
  \end{bmatrix}
  $
  \begin{enumerate}[label=\alph*)]
    \item Compute $\max_{\|x\|=1}|<A(x),x>$. Here are some hints:
    \begin{itemize}
      \item Convert the quadratic form $<A(x),x>$ into an equation in $cos(2\theta)$ and $sin(2\theta)$ as to satisfy the constraint $x^2 + y^2 = 1$
      \item This is optimization in on variable $\theta$ and it is ok to ignore optimize over the quadratic form instead of the absolute value of it.
      \item Find the solution in terms of $tan(2\theta)$ and use standard reference triangles to find the largest value of this quadratic form.
    \end{itemize}
    \item Prove the value above is the same as the largest absolute value of the eigenvalues of $A$: you find these eigenvalue by hand of course.
  \end{enumerate}
  \item Prove $T(x) = |<A(x),x>|$ is a continuous function of $x$ for $x \in (C([a,b]),\|\cdot\|_\infty)$ using the standard inner product on $C([a,b])$ and $(A(x))(t) = \int_a^b\:k(s,t)x(s)ds$ with $k$ a symmetric continuous function on $[a,b]\times[a,b]$
\end{enumerate}
\end{document}
