% SampleProject.tex -- main LaTeX file for sample LaTeX article
%
%\documentclass[12pt]{article}
\documentclass[11pt]{SelfArxOneColBMN}
% add the pgf and tikz support.  This automatically loads
% xcolor so no need to load color
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{matrix}
\usetikzlibrary{calc}
\usepackage{xstring}
\usepackage{pbox}
\usepackage{etoolbox}
\usepackage{marginfix}
\usepackage{xparse}
\setlength{\parskip}{0pt}% fix as marginfix inserts a 1pt ghost parskip
% standard graphics support
\usepackage{graphicx,xcolor}
\usepackage{wrapfig}
%
\definecolor{color1}{RGB}{0,0,90} % Color of the article title and sections
\definecolor{color2}{RGB}{0,20,20} % Color of the boxes behind the abstract and headings
%----------------------------------------------------------------------------------------
%	HYPERLINKS
%----------------------------------------------------------------------------------------
\usepackage[pdftex]{hyperref} % Required for hyperlinks
\hypersetup{hidelinks,
colorlinks,
breaklinks=true,%
urlcolor=color2,%
citecolor=color1,%
linkcolor=color1,%
bookmarksopen=false%
,pdftitle={preSpringBreakMeeting},%
pdfauthor={Peterson}}
%\usepackage[round,numbers]{natbib}
\usepackage[numbers]{natbib}
\usepackage{lmodern}
\usepackage{setspace}
\usepackage{xspace}
%
\usepackage{subfigure}
\newcommand{\goodgap}{
  \hspace{\subfigtopskip}
  \hspace{\subfigbottomskip}}
%
\usepackage{atbegshi}
%
\usepackage[hyper]{listings}
%
% use ams math packages
\usepackage{amsmath,amsthm,amssymb,amsfonts}
\usepackage{mathrsfs}
%
% use new improved Verbatim
\usepackage{fancyvrb}
%
\usepackage[titletoc,title]{appendix}
%
\usepackage{url}
%
% Create length for the baselineskip of text in footnotesize
\newdimen\footnotesizebaselineskip
\newcommand{\test}[1]{%
 \setbox0=\vbox{\footnotesize\strut Test \strut}
 \global\footnotesizebaselineskip=\ht0 \global\advance\footnotesizebaselineskip by \dp0
}
%
\usepackage{listings}

\DeclareGraphicsExtensions{.pdf, .jpg, .tif,.png}

% make sure we don't get orphaned words if at top of page
% or orphans if at bottom of page
\clubpenalty=9999
\widowpenalty=9999
\renewcommand{\textfraction}{0.15}
\renewcommand{\topfraction}{0.85}
\renewcommand{\bottomfraction}{0.85}
\renewcommand{\floatpagefraction}{0.66}
%
\DeclareMathOperator{\sech}{sech}

\input{setupsample}

\JournalInfo{Thesis Meeting, 1-\pageref{LastPage}, 2020} % Journal information
\Archive{Draft Version \today} % Additional notes (e.g. copyright, DOI, review/research article)

\PaperTitle{Thesis Meeting}
\Authors{Ian Davis\textsuperscript{1}}
\affiliation{\textsuperscript{1}\textit{John E. Walker Department of Economics,
Clemson University,Clemson, SC: email ijdavis@g.clemson.edu}}
%\affiliation{*\textbf{Corresponding author}: yournamehere@clemson.edu}  Corresponding author

\date{\small{Version 01142020 : Compiled ~\today}}

\Abstract{
Here are some things about where I am at with my model and my data and problems that I am running into or something like that.
}
\Keywords{
{\bf TBD} --
{\bf TBD} --
{\bf TBD} -- 
{\bf TBD} }
\newcommand{\keywordname}{Keywords}
%
\onehalfspacing
\begin{document}

\flushbottom

\addcontentsline{toc}{section}{Title}
\maketitle
\addcontentsline{toc}{section}{Table Of Contents}
\tableofcontents
\thispagestyle{empty}
\newpage
	
\section{Introduction}
\label{sec:introduction}

\noindent
Here, I will give some context regarding things the thoughts that have lead to where we are today and where \textit{some} of the literature is currently at. References to Laxminarayan will probably go here and there will be a lead in to what we consider to be the economic model

\section{Economic Model}
\label{sec:economic model}

\noindent
In order to more clearly draw the connection between change of patent status and change of antibiotic effectiveness, we first want to illustrate, at a theoretical level, our assumption of how they interact. All visits to a physician can be considered to have a corresponding probability that a given antbiotic will be prescribed inclusive of zero. The doctor is faced with two sequential decisions. First, should a prescription be made at all, and second, which antbiotic should be prescribed. In an ideal world, these decisions would be based entirely on how effective a drug may be at curing the affliction of the patient. However, a necessary condition of our model is that htis is not the case. We believe that a physician considers a great deal of characters of both the drug of interest and other close substitutes while making their decision. It is believed a relationship exists between the probability a drug is prescribed and the effectiveness of said drug, the price of said drug, the effectiveness of close substitutes, and the price of said substitutes. All of which are evaluated at a specific time period $t$
\begin{eqnarray}
  usage_t = f(\text{efficacy}_{i,t},\text{price}_{i,t},\text{efficacy}_{j,t},\text{price}_{j,t})
\end{eqnarray}
But an additional wrinkle is created when we consider 
\begin{eqnarray}
  \text{efficacy_t} = g(usage_{t-1})
\end{eqnarray}

%Sit on this
  % \text{Pr}(\text{prescription of drug}\; i\; |\;\text{symption set} \: x \: \text{at time} \: t)

%Discussion of the model will occur here but not of the statistical model and we will not be assuming functional form. Instead, we are going to carefully talk about what we think is occuring and why it would happen. Something about like going back to Laxminarayan and saying "Well this is how bacteria mutate so naturally this is how intellectual property laws could affect that." Again, we are not assuming functional form (but there is an important time element) so it'll be something like


%\begin{eqnarray} %no * because we may want to reference these
  %effectiveness_t = f(quality_t,quantity_{t-1}(price_{t-1},patentStatus_{t-1},...),...)
%\end{eqnarray}
%It could also be important to mention the different way's effectiveness could be measured but that may be best referenced here after a more flushed out discussion in the introduction.

\section{Data}
\label{sec:data}

\noindent
First we need to talk about our antibiotics and which one's we are sticking with and why. Throw out the pictures of cefotetan and maybe sulfamethazole. I guess I can bang out one or two new datasets pretty quickly so it would only be a difficulty regarding naming everything and playing around in my terminal.\\
\\
I might've jumped the gun. First, talk about all of the antibiotics we fist got data on from the critically important for human health list. Next, we narrowed down the list to ones that came off patently recentlyish. Then we looked for which ones would be the best to use.
\\
Next, we are really going to get in to the National Ambulatory Healthcare Survey. We are going to talk a little about how it \textit{was} formatted and a lot about how it \textit{is} formatted. The current format is crucial because it has to lay the groundwork for a discussion on what statistical models can be leveraged later on. From here we can talk about how we found specific drugs that were interesting and fit the model of how we thought it should look.\\
\\
It would be really nice to be able to speak briefly and in English about the one or two drugs I want to look at. Just to give context for what these things do and stuff.
\\
\noindent
Now, we can go into the question of tying it to resistance rates. I guess talk about (or rule out) the possibilities of using MIB's, MIC's, or aggregated antibiograms for a possible connection with resistance. 

\section{More Stuff}
\label{sec:more stuff}

\noindent
I definitely need some more stuff but I don't really know what it would be. I'll figure it out.\\
\\
Just wasting space\\
\\
More space\\
\\
Space\\
\\
Space

\section{One More Thing}
\label{sec:one more thing}
Here's another thing just so I can get some more pages.


\end{document}
