% pdflatex litNotes.tex
% bibtex litNotes.aux
% pdflatex litNotes.tex
% pdflatex litNotes.tex



\input{preamble}
\let\counterwithout\relax
\let\counterwithin\relax
\definecolor{maroon}{HTML}{4B0082}

\begin{document}

\noindent\textbf{Evaluation of Generic Antibiotic Usage Under the Perspective of Drug Cost} \cite{mercanoglu_evaluation_2018}\\
\begin{itemize}

\end{itemize}

\noindent\textbf{Off-label use of oral fluoroquinolone antibiotics in outpatient settings in the United States, 2006 to 2012} \cite{almalki_off-label_2016}.\\
\begin{itemize}
    \item \textbf{Paper warrents a careful read!}
    \item Uses NAMCS 2006-2012
    \item Study of how fluoroquinolone antibiotics are used in ambulatory settings
    \item Finds that many times the drugs are prescribed for indicators "in which the safety and the efficacy are not yet established."
\end{itemize}

\noindent\textbf{Trends in Antibiotic Prescribing for Adults in the United States—1995 to 2002} \cite{roumie_trends_2005}.\\
\begin{itemize}

\end{itemize}

\noindent\textbf{Outpatient Antibiotic Prescribing for Older Adults in the United States: 2011 to 2014} \cite{kabbani_outpatient_2018}.\\
\begin{itemize}

\end{itemize}

\noindent\textbf{Comparative analysis of the cost and effectiveness of generic and brand-name antibiotics: the case of uncomplicated urinary tract infection} \cite{lin_comparative_2017}.\\
\begin{itemize}
    \item Uses the Longitudinal Health Insurace Database of Taiwan to look at healthcare costs of individuals with UTIs
    \item Found individuals treated with generics had equivalent outcomes to those treated with brand names but at a much lower cost.
\end{itemize}

\noindent\textbf{Past, Present, and Future of Antibacterial Economics: Increasing Bacterial Resistance, Limited Antibiotic Pipeline, and Societal Implications} \cite{luepke_past_2017}.\\
\begin{itemize}

\end{itemize}

\noindent\textbf{A review of the differences and similarities between generic drugs and their originator counterparts, including economic benefits associated with usage of generic medicines, using Ireland as a case study} \cite{dunne_review_2013}.\\
\begin{itemize}
    \item Primarily focuses on Ireland but does have a section comparing US policy with Europe.
    \item Very good and specific definitions of generics in the United States, what is required by the FDA for approval, and meaning of biosimilarity.
    \item Cites source claiming generics are typically between 20-90\% cheaper than their originators. Source is from the European Union so a number for the United States needs to be found. 
\end{itemize}

\noindent\textbf{What do people really think of generic medicines? {A} systematic review and critical appraisal of literature on stakeholder perceptions of generic drugs} \cite{dunne_what_2015}.\\
\begin{itemize}

\end{itemize}

\noindent\textbf{Economic Savings Versus Health Losses: The Cost-Effectiveness of Generic Antiretroviral Therapy in the United States} \cite{walensky_economic_2013}.\\
\begin{itemize}
    \item Not very much to say on this paper. Uses a mathematical simulation to show that if all HIV positive individuals switched to a generic treatment savings are estimated to be \$920 Million.
    \item interesting but may not be very useful
\end{itemize}

\noindent\textbf{Comparative effectiveness of generic and brand-name medication use: A database study of US health insurance claims} \cite{desai_comparative_2019}.\\
\begin{itemize}
    \item Recent US study that found "comparable" results between patients using brand name and generic medications.
    \item Should be noted that the study used "Authorized Generics" which are identical in composition and appearance to brand names. Need to check if the Sulfamethoxazole-Trimethroprim fits this category.
\end{itemize}

\newpage

\bibliography{litNotes} 
\bibliographystyle{unsrt}

\end{document}