%Input preamble
\input{preamble}
\let\counterwithout\relax
\let\counterwithin\relax
\definecolor{maroon}{HTML}{4B0082}

\begin{document}

\noindent \textbf{8190: Masters Thesis Research}\\
\noindent \textbf{22 May 2020}\\
\noindent Instructor: Scott Templeton \\
e-mail: stemple@clemson.edu\\

\noindent \textbf{Sulfamethoxazole/Trimethoprim}\\
\\
Sulfamethoxazole/Trimethoprim is a combination antibiotic from the class antimetabolite/sulfonamide. The brands of the drug include Bactrim, Bactrim DS, Septra, and Septra DS and the generic form entered the American market in July of 2012. The antibiotic works through sulfamethoxazole inhibiting bacterial synthesis of dihydrofolic acid by competing with \textit{para}-aminobenzoic acid and trimethoprim blocking the production of tetrahydrofolic acid from dihydrofolic acid by binding to and reversibly inhibiting the required enzyme, dihydrofolate reductase.\\
\\
The drug has FDA approval to fight urinary tract infections, acute otitis media (ear infections), acute exacerbations of chronic bronchitis in adults, Shigellosis, treatment and prophylaxis of \textit{Pneumocystis jirovecii} pneumonia, and Traveler's diarrhea in a adults. The antibiotic is also used for infections due to \textit{Listeria, Nocardia, Salmonella, Brucella, Paracoccidioides,} melioidosis, \textit{Burkholderia, Stenotrophomonas,} cyclospora, isospora, Whipple's disease, and alterntive therapy for toxoplasmosis and community-acquired MRSA skin infections.\\
\\
Due to possible interference with folic acid metabolism, there is potential risk to the fetus if taken during pregnancy. Hence, it is only recommended that the drug is taken during pregnancy if the potential risks are outweighed by the possible benefits.\\

\noindent \textbf{National Ambulatory Medical Care Survey}\cite{myrick_understanding_nodate}\\
\\
Data used are from the National Ambulatory Medical Care Survey (NAMCS) which is a nationally representative survey of outpatient medical visits. Included in the scope of the survey are freestanding clinics/urgicenters, community health centers, mental health centers, health maintenance organizations,  non-federal government clinics, family practice plans, and private solo or group practices. Not included are hospital emergency or outpatient departments, ambulatory surgicenters, institutional settings such as schools or prisons, industrial outpatient facilities, clinics operated by the federal government, and laser vision surgery centers.\cite{hing_basic_nodate}. The surveys include patient, visit, and provider characterists and weights are provided in order to create national estimates.\\
\\
I pool results from the years 2006 to 2016 and drop variables which are not consistently tracked across this time frame. For the specific cases of diagnoses and prescriptions, the maximum amount of available entries increased during the study period. The 2006 NAMCS survey allowed for collection of three unique diagnoses and eight unique prescriptions. In 2012, the maximum number of drugs collected was raised to twelve and 2014 saw that number increased again to thirty along with increasing the number of maximum diagnoses to 5. 

\newpage
\bibliography{dataAndBackGround} 
\bibliographystyle{unsrt}

\end{document}

% Use dash instead of forward slash "Sulfamethoxazole-Trimethoprim" 
% Is the class/class a subclass or synonym. 
% Quote the stuff that you don't know if even write about it.

% Use the less well known name in quotations "Ear Infections (Acute Otitis Media)
% My big poorly worded sentance could most likely be taken out%Input preamble

%https://ftp.cdc.gov/pub/Health_Statistics/NCHS/Dataset_Documentation/NHAMCS/doc17_ed-508.pdf

%\textbf{Sources}
%\begin{enumerate}
%    \item National Center for Health Statistics.2017 NHAMCS micro-data file documentation. Hyattsville, MD.
%
%    \item Trends in Opioids Prescribed at Discharge From Emergency Departments Among Adults: United States, 2006-2017
%
%    \item Schlossberg D. L., \& Samuel, R. (2017). Antibiotics Manual: A Guide to Commonly Used Antimicrobials.

%\end{enumerate}