%Input preamble

%https://ftp.cdc.gov/pub/Health_Statistics/NCHS/Dataset_Documentation/NHAMCS/doc17_ed-508.pdf

\input{preamble}
\let\counterwithout\relax
\let\counterwithin\relax
\definecolor{maroon}{HTML}{4B0082}

\begin{document}
Data used are from the Emergency Department public use micro-data files of the National Hospital Ambulatory Medical Care Survey (NHAMCS) from 2006-2016. "The NHAMCS is a national probability sample survey of visits to hospoital outpatient and emergency departments and hospital-based ambulatory surgery centers, conducted by the National Center for Health Statistics" (1). The surveys are portion of larger set of surveys known as the National Health Care Surveys which are collected in order to measure health care utilization across various providers.

Data are collected from emergency and outpatient departments from all 50 states and Washington D.C. excluding Federal, military, and Veterens Administration hospitals. A four stage probability design is used to create the sample starting with the national level then moving to the hospital level, outpatient clinic and emergency service area level, and finally, the visit level. Response rates ranged from 70.8\% in 2015 to 93.1\% 2008 (2).

The 


\begin{enumerate}
    \item National Center for Health Statistics.2017 NHAMCS micro-data file documentation. Hyattsville, MD.

    \item Trends in Opioids Prescribed at Discharge From Emergency Departments Among Adults: United States, 2006-2017
\end{enumerate}

\end{document}