% SampleProject.tex -- main LaTeX file for sample LaTeX article
%
%\documentclass[12pt]{article}
\documentclass[11pt]{SelfArxOneColBMN}
% add the pgf and tikz support.  This automatically loads
% xcolor so no need to load color
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{matrix}
\usetikzlibrary{calc}
\usepackage{xstring}
\usepackage{pbox}
\usepackage{etoolbox}
\usepackage{marginfix}
\usepackage{xparse}
\setlength{\parskip}{0pt}% fix as marginfix inserts a 1pt ghost parskip
% standard graphics support
\usepackage{graphicx,xcolor}
\usepackage{wrapfig}
%
\definecolor{color1}{RGB}{0,0,90} % Color of the article title and sections
\definecolor{color2}{RGB}{0,20,20} % Color of the boxes behind the abstract and headings
%----------------------------------------------------------------------------------------
%	HYPERLINKS
%----------------------------------------------------------------------------------------
\usepackage[pdftex]{hyperref} % Required for hyperlinks
\hypersetup{hidelinks,
colorlinks,
breaklinks=true,%
urlcolor=color2,%
citecolor=color1,%
linkcolor=color1,%
bookmarksopen=false%
,pdftitle={SampleProject},%
pdfauthor={Peterson}}
%\usepackage[round,numbers]{natbib}
\usepackage[numbers]{natbib}
\usepackage{lmodern}
\usepackage{setspace}
\usepackage{xspace}
%
\usepackage{subfigure}
\newcommand{\goodgap}{
  \hspace{\subfigtopskip}
  \hspace{\subfigbottomskip}}
%
\usepackage{atbegshi}
%
\usepackage[hyper]{listings}
%
% use ams math packages
\usepackage{amsmath,amsthm,amssymb,amsfonts}
\usepackage{mathrsfs}
%
% use new improved Verbatim
\usepackage{fancyvrb}
%
\usepackage[titletoc,title]{appendix}
%
\usepackage{url}
%
% Create length for the baselineskip of text in footnotesize
\newdimen\footnotesizebaselineskip
\newcommand{\test}[1]{%
 \setbox0=\vbox{\footnotesize\strut Test \strut}
 \global\footnotesizebaselineskip=\ht0 \global\advance\footnotesizebaselineskip by \dp0
}
%
\usepackage{listings}

\DeclareGraphicsExtensions{.pdf, .jpg, .tif,.png}

% make sure we don't get orphaned words if at top of page
% or orphans if at bottom of page
\clubpenalty=9999
\widowpenalty=9999
\renewcommand{\textfraction}{0.15}
\renewcommand{\topfraction}{0.85}
\renewcommand{\bottomfraction}{0.85}
\renewcommand{\floatpagefraction}{0.66}
%
\DeclareMathOperator{\sech}{sech}

\input{setupsample}

\JournalInfo{MATH 8210:  Homework Two, 1-\pageref{LastPage}, 2020} % Journal information
\Archive{Draft Version \today} % Additional notes (e.g. copyright, DOI, review/research article)

\PaperTitle{MATH 8210 Homework Two}
\Authors{Your Name Here\textsuperscript{1}}
\affiliation{\textsuperscript{1}\textit{School of Mathematical and Statistical Sciences,
Clemson University,Clemson, SC: email yournamehere@clemson.edu}}
\affiliation{*\textbf{Corresponding author}: yournamehere@clemson.edu} % Corresponding author

\date{\small{Version ~\today}}
\Abstract{Some problems metric spaces}
\Keywords{}
\newcommand{\keywordname}{Keywords}
%
\onehalfspacing
\begin{document}

\flushbottom

\addcontentsline{toc}{section}{Title}
\maketitle

\renewcommand{\theexercise}{\arabic{exercise}}%

\noindent
Here are some questions about equivalence class stuff.
Enjoy!


\begin{exercise}
Let $[a,b]$, with $a < b$, be an interval and let $c$ satisfy
$a < c < b$.
Define the metric space
$(\widetilde{RI}([a,b]), \widetilde{d_1})$
carefully.  If $f$ is defined by
\begin{eqnarray*}
f(x) &=&
\left \{
\begin{array}{ll}
H, & a \leq t < c\\
L, & c \leq t \leq b
\end{array}
\right .
\end{eqnarray*}
\noindent
where both $L$ and $H$ are positive numbers.
\noindent
Explain the difference between $f$ and its equivalence
class $[f]$ in $(\widetilde{RI}([a,b]), \widetilde{d_1})$.
\end{exercise}

\begin{solution}
Your solution here.
\end{solution}
	
\begin{exercise}
Let $[a,b]$, with $a < b$, be an interval and let $c$ satisfy
$a < c < b$.
Define $f$ by
\begin{eqnarray*}
f(x) &=&
\left \{
\begin{array}{ll}
H, & a \leq t < c\\
L, & c \leq t \leq b
\end{array}
\right .
\end{eqnarray*}
\noindent
where both $L$ and $H$ are positive numbers.
Prove there is a  Cauchy Sequence of continuous functions, $(x_n)$
under $d_1$ which converges to $f$.  Then explain why the sequence of
equivalance classes $([x_n])$ converges to $[f]$ in
$(\widetilde{RI}([a,b]), \widetilde{d_1})$.
\end{exercise}

\begin{solution}
Your solution here.
\end{solution}

\begin{exercise}
Let $[a,b]$, with $a < b$, be an interval and let 
$P = \{t_0 = a, t_1, \ldots, t_{n-1}, t_n = b\}$
be a partition of $[a,b]$ and let
$E = \{s_0,s_1, \ldots, s_{n-1}\}$
be any evaluation set; i.e. each $s_i$ is a point in the
interval $[t_i, t_{i+1}]$.  Let $f$ be a Riemann Integrable function on
$[a,b]$.
If $f_{PE}$ is defined by
\begin{eqnarray*}
f_{PE}(x) &=&
\left \{
\begin{array}{ll}
f(s_i), & t_i \leq t < t_{i+1}, \quad 0 \leq i \leq n-1\\
f(s_{n-1}), &  t_{n-1} \leq t \leq b = t_n
\end{array}
\right .
\end{eqnarray*}
\noindent
\noindent
Explain the difference between $f_{PE}$ and its equivalence
class $[f_{PE}]$ in $(\widetilde{RI}([a,b]), \widetilde{d_1})$.
\end{exercise}

\begin{solution}
Your solution here.
\end{solution}
	
\begin{exercise}
For the function $f_{PE}$ in the previous exercise, 
prove there is a  Cauchy Sequence of continuous functions, $(x_n)$
under $d_1$ which converges to $f_{PE}$.  Then explain why the sequence of
equivalance classes $([x_n])$ converges to $[f_{PE}]$ in
$(\widetilde{RI}([a,b]), \widetilde{d_1})$.
\end{exercise}

\begin{solution}
Your solution here.
\end{solution}

\begin{exercise}
For the function $f_{PE}$ above, 
prove $f_{PE}$ is Riemann Integrable and $\int_a^b f_{PE}(t) dt = S(f,P,E)$
where $S((f,P,E)$ is the Riemann Sum of $f$ for partition $P$ and evaluation set $E$.
\end{exercise}

\begin{solution}
Your solution here.
\end{solution}

\begin{exercise}
Let $P_n$ and $E_n$ be a sequence of partitions and evaluation sets
of the interval $[a,b]$ with $a < b$ and let $f$ be a Riemann Integrable function
on $[a,b]$.  From the previous exercises, there is a Cauchy Sequence of
continuous functions $(x_n^m)$ for each $n$ which converges in 
$(\widetilde{RI}([a,b]), \widetilde{d_1})$ to $[f_{P_n,E_n}]$.
For convenience, let $f_n = f_{P_n,E_n}$.  Then we know
$f_n$ is Riemann Integrable and $\int_a^b f_n(t) dt = S(f,P_n,E_n)$.
From the Riemann Approximation Theorem, if $\| P_n\| \rightarrow 0$,
where $\| P_n\|$ is the norm of the partition $P_n$, it follows that
$d_1(f_n,f) \rightarrow 0$.  \\

\noindent
For a given $\epsilon > 0$,
since $d_1(x_j^m,f_j) \rightarrow 0$, prove we can find an index $n_j$ so that
$d_1(x_j^{n_j},f_j) < \frac{\epsilon}{2}$ for all $j$.  Then prove there is an $N$ so
\begin{eqnarray*}
d_1(x_j^{n_j},f) &<& d_1(x_j^{n_j},f_j) + d_1(f_j,f) < \epsilon
\end{eqnarray*}
\noindent
for all $j > N$.  This shows there is a Cauchy Sequence of
continuous functions $(x_j^{n_j})$ which satisfies
$\widetilde{d_1}( [x_j^{n_j}], [f] ) \rightarrow 0$.
{\bf So we have a way of identifying any Riemann Integrable
function with an Cauchy Sequence of equivalence classes
of continuous functions}.
\end{exercise}

\begin{solution}
Your solution here.
\end{solution}


	
\end{document}