% SampleProject.tex -- main LaTeX file for sample LaTeX article
%
%\documentclass[12pt]{article}
\documentclass[11pt]{SelfArxOneColBMN}
% add the pgf and tikz support.  This automatically loads
% xcolor so no need to load color
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{matrix}
\usetikzlibrary{calc}
\usepackage{xstring}
\usepackage{pbox}
\usepackage{etoolbox}
\usepackage{marginfix}
\usepackage{xparse}
\setlength{\parskip}{0pt}% fix as marginfix inserts a 1pt ghost parskip
% standard graphics support
\usepackage{graphicx,xcolor}
\usepackage{wrapfig}
%
\definecolor{color1}{RGB}{0,0,90} % Color of the article title and sections
\definecolor{color2}{RGB}{0,20,20} % Color of the boxes behind the abstract and headings
%----------------------------------------------------------------------------------------
%	HYPERLINKS
%----------------------------------------------------------------------------------------
\usepackage[pdftex]{hyperref} % Required for hyperlinks
\hypersetup{hidelinks,
colorlinks,
breaklinks=true,%
urlcolor=color2,%
citecolor=color1,%
linkcolor=color1,%
bookmarksopen=false%
,pdftitle={finalExam},%
pdfauthor={Ian Davis}}
%\usepackage[round,numbers]{natbib}
\usepackage[numbers]{natbib}
\usepackage{lmodern}
\usepackage{setspace}
\usepackage{xspace}
%
\usepackage{subfigure}
\newcommand{\goodgap}{
  \hspace{\subfigtopskip}
  \hspace{\subfigbottomskip}}
%
\usepackage{atbegshi}
%
\usepackage[hyper]{listings}
%
% use ams math packages
\usepackage{amsmath,amsthm,amssymb,amsfonts}
\usepackage{mathrsfs}
%
% use new improved Verbatim
\usepackage{fancyvrb}
%
\usepackage[titletoc,title]{appendix}
%
\usepackage{url}
%
% Create length for the baselineskip of text in footnotesize
\newdimen\footnotesizebaselineskip
\newcommand{\test}[1]{%
 \setbox0=\vbox{\footnotesize\strut Test \strut}
 \global\footnotesizebaselineskip=\ht0 \global\advance\footnotesizebaselineskip by \dp0
}
%
\usepackage{listings}

\DeclareGraphicsExtensions{.pdf, .jpg, .tif,.png}

% make sure we don't get orphaned words if at top of page
% or orphans if at bottom of page
\clubpenalty=9999
\widowpenalty=9999
\renewcommand{\textfraction}{0.15}
\renewcommand{\topfraction}{0.85}
\renewcommand{\bottomfraction}{0.85}
\renewcommand{\floatpagefraction}{0.66}
%
\DeclareMathOperator{\sech}{sech}

\input{setupsample}

\JournalInfo{MATH 8210: Final Exam, 1-\pageref{LastPage}, 2020} % Journal information
\Archive{Draft Version \today} % Additional notes (e.g. copyright, DOI, review/research article)

\PaperTitle{MATH 8210 Final Exam}
\Authors{Ian Davis\textsuperscript{1}}
\affiliation{\textsuperscript{1}\textit{John E. Walker Department of Economics,
Clemson University,Clemson, SC: email ijdavis@g.clemson.edu}}
%\affiliation{*\textbf{Corresponding author}: yournamehere@clemson.edu} % Corresponding author

\date{\small{Version ~\today}}
\Abstract{Final Exam}
\Keywords{}
\newcommand{\keywordname}{Keywords}
%
\onehalfspacing
\begin{document}
\flushbottom

\addcontentsline{toc}{section}{Title}
\maketitle

\renewcommand{\theexercise}{\arabic{exercise}}
\begin{exercise}
  For the data
  \begin{eqnarray*}
    f(t) &=&
    \left \{
    \begin{array}{ll}
     0, & a \leq t < c\\
     H, & c \leq t \leq b
    \end{array}
    \right .
  \end{eqnarray*}
\noindent
for some $a < c < b$. Let $f_1(t) = 0$ on $[1,c]$ and $f_2(t) = H$. Solve $(\mathbf{L} - \lambda_0\mathbf{I})(\mathbf{u_1}) = \mathbf{f_1}, \; (\mathbf{L} - \lambda_0\mathbf{I})(\mathbf{u_2}) = \mathbf{f_2}$ and discuss how these solutions compare to the solution $(\mathbf{L} - \lambda_0\mathbf{I})(\mathbf{u}) = \mathbf{f}$. Explain how we obtain a solution which satisfies $(\mathbf{L} - \lambda_0\mathbf{I})(\mathbf{u}) = \mathbf{f}$ as a classical differential equation on [a,b] except at c; i.e. $(\mathbf{L} - \lambda_0\mathbf{I}(\mathbf{u}) = \mathbf{f}$ a.e.
\end{exercise}

\begin{exercise}
  See Section 13.7 and repeat the problem with $L =6$ for $k = 1$ and $k = 2$. Perform the full derivation using the Frobenius technique for power series solutions before doing the code. 
\end{exercise}

\begin{exercise}
  Find the eigenfunctions and eigenvalues for the Bessel's Equation as discussed above on [0,7] for $k =2$ and use them to find the best approximation to $f(x) = 3sin(4x)e^{0.7x}$
\end{exercise}

\begin{exercise}
  Let $G(V,E)$ be a graph with $|V|$ nodes and $|E|$ edges. Let $N = |V|$ be the number of nodes. Then a fully connected graph with no self connections has at most $N^2 - N$ edges. Then if $i$ and $j$ are nodes, the edge $E_{i \rightarrow j}$ is the edge cost connecting node $i$ to node $j$. Assume all the edge costs are positive but the cost $E_{i \rightarrow j}$ is not necessarily ther same as the cost $E_{j \rightarrow i}$. For any path that connects node $i$ to node $j$, dynamic programming is an algorithm which will calculate the minimum cost path. Let $d_{ij}$ be the minimum cost path connecting node $i$ and node $j$ where we set $d_{ii} = 0$ for all nodes $i$. Prove $(V,d)$ is a metric space.
\end{exercise}

\begin{exercise}
  A symmetric bilinear map between the vector spaces $V$ adn $W$ is a mapping that satisfies IP1, IP2, and IP3 for an inner product. So clearly, any inner product is also a symmetric bilinear map. Define $\phi: \ell^p \times \ell^q \rightarrow \Re$ by $\phi_{pq}(x,y) = \sum_{n = 1}^\infty\:x_iy_j$.
  \begin{itemize}
    \item Prove $\phi_{pq}$ is a well defined symmetric bilinear map for the conjugate indices $p$ and $q$.
    \item Prove 
    \begin{eqnarray*}
      \sup_{\|x\|_p=1,\|y\|_p=1}|\phi_{pq}(x,y)| \leq 1
    \end{eqnarray*}
    \item Prove $\phi_{22}$ is an inner product.
  \end{itemize}
\end{exercise}
\end{document}